\section{Comparison} \label{tool:sec:compT}
This section will compare the result of the research. Therefore, a calculation of the costs ranges with the average and the limits, a summary is done and afterwards the comparison.

First of all the calculation for the costs criteria is done. The average is the sum of all prices for one document divided by the number of tools taken into account. In the case there is no price information given, the tool is ignored for the calculation. All number are rounded up to two decimals behind the comma.
\begin{center}
	\fbox{
		\parbox[centering]{10cm}{$\sum$ = 15,88 + 4,93 + 7,92 + 7,63 + 1,25 + 0,83 = 38,44 \newline
		$\varnothing = \sum / \# tools$ = 38,44/6 = 6,41	}
	}
\end{center}

This leads to the following limits, given in table \ref{tool:tab:limitscosts}:
\begin{table}[h!]
	\begin{tabular}{|c|c|c|c|c|} \hline
		Limit & -50\% & -25\% & $ \varnothing$ & +25\% \\ \hline
		Value & 3,21 & 4,81 & 6,41 & 8,02 \\ \hline
	\end{tabular}
	\centering
	\caption{Limits value for cost comparison}
	\label{tool:tab:limitscosts}
\end{table}

Based on the criteria defined in section \ref{sec:criteria} and the calculation did above, the different tools are summarized with the regarding weight. That is done in Table \ref{tool:tab:summary}. In the case there is no information available a ''/'' is used to visualize it.

%\begin{table}[h!]
	\begin{longtable}{|c|c|c|c|c|c|c|c|c|c|} \hline
		Criterion & \multicolumn{9}{c}{Tool} \\
				& \rotatebox{90}{Wacom} & \rotatebox{90}{DocuSign} & \rotatebox{90}{HelloSign} & \rotatebox{90}{SignDoc} & \rotatebox{90}{Adobe Sign} & \rotatebox{90}{SignNow} & \rotatebox{90}{eSign Live} & \rotatebox{90}{PandaDoc} & \rotatebox{90}{eSignAnyWhere} \\ \hline
		Integration & - - & + + & + + & + & + + & + + & + & + + & + \\ \hline
		Device Independent & - - & + + & + + & - - & + + & + + & + + & + + & + + \\ \hline
		Usability & / & + & o &  / & o & o & o & o & + \\ \hline
		Costs & / & + & - & / & / & + + & - & - - & + + \\ \hline
		Accepted file formats & / &  + & + + & / & + & + + & + + & + & + \\ \hline
		Operating mode & / & + + & + + & o & + + & + + & + + & + + & + + \\ \hline
		Additional security & / & + + & + & / & + + & + & + & - - & + + \\ \hline
		Legal aspects & / & + + & + + & / & / & + + & + + & + + & + + \\ \hline 
%	\centering
	\caption{Summary of tools based on criteria}
	\label{tool:tab:summary}
	\end{longtable}
%	\centering
%	\caption{Summary of electronic signature types based on criteria}
%	\label{tab:summary}
%%\end{table}

To make a better comparison of the different \gls{es} types, a translation from weighting to points is done in table \ref{tool:Tab:Translation} which is used in a later calculation.

\begin{table}[h!]
	\begin{tabular}{|c|c|c|c|c|c|c|} \hline
		Weight & / & - - & - & o & + & + + \\ \hline
		Points & -10 & -2 & -1 & 0 & 1 & 2 \\ \hline
	\end{tabular}
	\centering
	\caption{Translation of weights in points}
	\label{tool:Tab:Translation}
\end{table}

To get a complete image of the result the translated weights are multiplied with the importance of the criterion. To make it visible:
\begin{center}
	\fbox{
		\parbox[centering]{9cm}{\textit{Sum = Importance of Criterion * Points of Weight}}
	}
\end{center}
The result of that calculation is presented in table \ref{tool:Tab:comp}. If a tool has more than one ''/'', it is ignored, due to the 

%\begin{table}[h!]
	\begin{longtable}{|c|c|c|c|c|c|c|} \hline
		Criterion & \multicolumn{6}{c}{Tool} \\
		 & \rotatebox{90}{DocuSign} & \rotatebox{90}{HelloSign} & \rotatebox{90}{SignNow} & \rotatebox{90}{eSign Live} & \rotatebox{90}{PandaDoc} & \rotatebox{90}{eSignAnyWhere} \\ \hline
		Integration 	      & 16 & 16 & 16 & 8  & 16  & 8 \\ \hline
		Device Independent    & 14 & 14 & 14 & 14 & 14  & 14 \\ \hline
		Usability 		   	  & 6  & 0  & 0  & 0  & 0   & 6 \\ \hline
		Costs 			   	  & 5  & -5 & 10 & -5 & -10 & 10 \\ \hline
		Accepted file formats & 4  & 8  & 8  & 8  & 4   & 4 \\ \hline
		Operating mode 		  & 6  & 6  & 6  & 6  & 6   & 6 \\ \hline
		Additional security   & 4  & 2  & 2  & 2  & -8  & 4 \\ \hline
		Legal aspects         & 2  & 2  & 2  & 2  & 2   & 4 \\ \hline 
		Total Sum             & 57 & 43 & 58 & 35 & 24  & 56 \\ \hline
%	\centering
	\caption{Comparison of tools}
	\label{tool:Tab:comp}
	\end{longtable}
%	\centering
%	\caption{Comparison of electronic signature types}
%	\label{Tab:comp}
%\end{table}
