\chapter{Project Description}
The following chapter gives an overview about the project task and the background of it.

\section{Background}
The first plan was to create a contract management system for the customer Wacom, which produces mobile devices with interactive displays that can be used to make graphics or to sign documents \footnote{https://www.wacom.com/en-de}. But currently they develop a new \gls{SDK} that will be finished earliest in July 2018.

Than a contact to the Finance and Sales department was made. They currently want to setup a new \gls{erp}, because the old \gls{erp} does not fit the requirements any more. One big aspect for them is to reduce the paper work and automate or simplify several processes regarding making invoices, conclude contracts, starting projects and storing data at only one point for all departments.

\section{Task \& Idea}
The idea of the task is to introduce the \gls{es} with a general usage by \gls{cc}. Currently they use the \gls{es} partly, but not in all areas possible.
This means that all possible contracts and offers should be signed with the \gls{es} and stored digital, so that the paperless office can be created. Included in the task is the creation of a workflow, that automates the process of subscribing regrading the signing guideline of \gls{cc} so that cost for managing could be reduced and the response time is increased.

In the case that there is time left the aspects of creation of contracts and offers based on templates and customer depending information could be added to the workflow and the archiving of contracts regarding the regulations based from the governance and \gls{cc}. For the realization already existing tools should be used in the best case.

\section{Scope}
 The main focus is the creation of a process for the electronic signing of documents. Additional the writing of the bachelor thesis is part of this focus. Only in the case that time is left until the end of the internship additional functionality is to be implemented like achieving the signed documents and the template creation of contracts and offers.

\section{Expected Results}
At least the workflow for subscribing documents based on regulations should be implemented in a way that the most steps are done automatically. Additional the product should be maintainable and extensible, in the sense that additional functionality could be implemented or the product integrated in the new \gls{erp}.

\section{Deliverables} 
At the end of the internship a working process should be implemented. That also needs to be documented in the sense that other developer can maintain the implemented process. Also a user manual should be created for the user of the process. 