\chapter{Introduction}
To finish the study course Software Engineering from the Fontys Hogeschool Techniek en Logistiek an bachelor thesis internship needs to be done. It starts at the 1st February 2018 at \gls{cc} in Solingen and ends at the 30th June 2018.
This document gives an overview about the company, the project information and the planning of the project.

The structure is the following: First the company \gls{cc} is described, than the project information are explained followed by the general project activities and finally the concrete planning containing deliverables, quality assurance and risk management is described. 

\section{codecentric AG}
\Gls{cc} was founded 2005 in Solingen and is focused on the agile development of software and the usage of innovative technology\footnote{https://www.codecentric.de/ueber-uns/unternehmen/}. The products distributed by \gls{cc} are: 
\begin{itemize}
	\item Services in \gls{IT}-Technology
	\item Consultancy service for software and performance
	\item Software development
	\item Trainings and workshops for developed software
\end{itemize}
At the moment \gls{cc} has fifteen sites in Europe and about 400 employees. Also \gls{cc} has two subsidiary start-ups \glspl{cd} and Instana\footnote{https://www.codecentric.de/ueber-uns/befreundete-startups/} and a lot of partners e.g. Scrum.org or elastic\footnote{https://www.codecentric.de/ueber-uns/partner/}.
That leads to many different competences with new technology like \textit{Internet of Things}, \textit{Big Data}, \textit{Continuous Delivery} and more.
A lot of customers from several areas and size use this competences and products.

\section{Site in Solingen}
In Solingen is the head quarter of \gls{cc} with space for 200 employees. Different departments are located here, like Finance, Sales, \gls{ds} and a team \gls{cd}.   
The bachelor thesis is executed in the department \gls{ds}. The team from \gls{ds} has currently a size of around fifteen members.

The project is for the administration from \gls{cc}. That includes mostly the departments Finance, Sales and Human Resources, but also other departments could be influenced through the project.

\section{Organization \& Infrastructure}
The whole company works with an agile approach and uses \gls{SCRUM} as their project management framework. Also they have a low hierarchy. The digital communication is done over SLACK, a wiki and mail. It exists a lot of more tools, but these are the most used.

To implement their solutions they use many different programming languages like Java, ASP.NET, R, VBA. Therefore, different frameworks and external partner software is used to realize their projects.