\section{Questions}

In this research the question will be answered which available tool or technology fits best the requirements of \gls{cc} to sign documents electronically to work more efficient. The  question will be answered through an internet research. Tools will be selected based on the information of different comparison portals and the information provided by the company itself. Furthermore, there will be some testing of the functionalities if possible to prove the usability for \gls{cc}. 

For the testing of the functional requirements like order of singing and the simple usage the preset up is to creation of three test mail addresses and three documents of the format \gls{pdf}, Microsoft word and Open Office writer. The real testing is based on the following steps:
\begin{enumerate}
	\item Register with master mail address to the tool.
	\item Upload the document.
	\item Enter other mail address to sign document.
	\item Select order of signing if possible.
	\item Add fields to sign if needed.
	\item Sign document with master mail address.
	\item Release document for other mail addresses.
	\item Do one of those steps:
	\begin{enumerate}
		\item Try to sign against order.
		\item Try to decline of document signing.
		\item Sign document with unknown account.
		\item Sign document with known accountt. 
	\end{enumerate}
	\item Check current state of the process.
	\item In the case the document is signed by all, check the availability of the document and download it.
\end{enumerate}