\newacronym{aes}{AES}{Advanced Electronic Signature}
\newacronym{api}{API}{Appliaction Programming Interface}
\newacronym{app}{App}{Application}
\newacronym{bgb}{BGB}{Bürgerliches Gesetzbuch (Civil Law Code from Germany)}
\newacronym{bs}{BS}{Biometric Signature}
\newacronym{bpmn}{BPMN}{Business Procress Modeling and Notation}
\newacronym{cc}{cc}{codecentric AG}
\newacronym{cd}{CD}{CenterDevice}
\newacronym{cms}{CMS}{Contract Management System}
\newacronym{db}{DB}{Database}
\newacronym{eea}{EEA}{European Economic Area}
\newacronym{eidas}{eIDAS}{electronic IDentification, Authentication and trust Services}
\newacronym{erp}{ERP}{Enterprise Resource Planning System}
\newacronym{es}{ES}{Electronic Signature}
\newacronym{eu}{EU}{European Union}
\newacronym{gtct}{GTCT}{General Terms and Conditions of Trade}
\newacronym{hr}{HR}{Human Resources}
\newacronym{IT}{IT}{Information Technology}
\newacronym{ldap}{LDAP}{Lightweight Directory Access Protocol}
\newacronym{mb}{MB}{Mega Byte}
\newacronym{mvc}{MVC}{Model View Controller Pattern}
\newacronym{nda}{NDA}{Non-Disclosure Agreement}
\newacronym{op}{OP}{On-Premise}
\newacronym{os}{OS}{Operating System}
\newacronym{PDF}{PDF}{Portable Document Format}
\newacronym{pki}{PKI}{Public-Key Infrastructure}
\newacronym{qes}{QES}{Qualified Electronic Signature}
\newacronym{rest}{REST}{Representational State Transfer}
\newacronym{saas}{SaaS}{Software as a Service}
\newacronym{ses}{SES}{Simple Electronic Signature}
\newacronym{sdk}{SDK}{Software Development Kit}
\newacronym{sms}{SMS}{Short Message Service}
\newacronym{sql}{SQL}{Structured Query Language}
\newacronym{uml}{UML}{Unified Modeling Language}
\newacronym{usa}{USA}{United States of America}
\newacronym{xml}{XML}{Extended Markup Language}


\newglossaryentry{app}{name={app}, description={Application Software \newline
		An application for all kinds of computer, in this document specific for mobile devices.}}
\newglossaryentry{api}{name={API},description={Application Programming Interface \newline
		Defined	interface for the communication to the tool or software that provides the interface.}}
\newglossaryentry{ds}{name={digital signature},description={The digital fingerprint of a digital document, also called Hash value}}
\newglossaryentry{eidas}{name={eIDAS},description={Regulation from European  parliament and council regarding electronic identification and trust services for  electronic  transactions  in  the  internal  market  and repealing  Directive  1999/93/EC.}}
\newglossaryentry{es}{name={electronic signature},description={The electronic signing of digital documents.}}
\newglossaryentry{gdpr}{name={GDPR},description={General Data Protection Regulation \newline Regulation from the European Union regarding data processing, storage and handling. Valid since 25th of May 2018.}}
\newglossaryentry{sc}{name={smartcard},description={A card with a chip on it, that stores data e.g. biometric data or certificates. It compares access data like a personal identification number with input data. Only if the data match each other, the user is identified and the rest of the data stored is accessible.}}
\newglossaryentry{SCRUM}{name={SCRUM},description={Project and product management model with the approach of an agile working process.}}
\newglossaryentry{SDK}{name={SDK},description={Software Development Kit \newline
		Collection of tools, documentation and libraries for software development.}}


\printglossaries